Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-02-19 strang/paper.tex
more updates

In \cite{castro_sdc}, we introduced a test problem where we could
measure the convergence of a reacting hydrodynamics problem via
Richardson extrapolation---this was an acoustic pulse with helium
burning via $3-\alpha$ and
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  Those tests focused on
SDC coupling and showed that we can get overall 4th order in space and
time convergence.  Here we run the same test with Strang coupling,
looking at the various approaches at incorporating a temperature
equation in the reactive portion of the update.

@@

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}), 
          SymPy \citep{sympy}
         }

>>>>

In \cite{castro_sdc}, we introduced a test problem where we could
measure the convergence of a reacting hydrodynamics problem via
Richardson extrapolation---this was an acoustic pulse with helium
burning via $3$-$\alpha$ and
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  Those tests focused on
SDC coupling and showed that we can get overall 4th order in space and
time convergence.  Here we run the same test with Strang coupling,
looking at the various approaches at incorporating a temperature
equation in the reactive portion of the update.

For each method, we run the \castro\ {\tt reacting\_convergence} test
problem at 5 resolutions: $64^2$, $128^2$, $256^2$, $512^2$, and
$1024^2$.  We then compute four errors between adjacent resolutions by
coarsening the finer resolution run, and computing the $L_1$ norm over
all zones.  Figure~\ref{thefigure} shows the norm of the error
vs.\ the coarse run resolution.  Guidelines showing ideal first and
second order convergence are shown.

@@

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          VODE \cite{vode}
         }
